---
title: "CEPP Ops Increment 1 - Round 2 Modeling"
output: 
  html_document: 
    keep_md: no
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      message=FALSE,
                      warning=FALSE)
```

## iModel Targets 

**TO DO **

*Insert explanatory text of iModel (inputs/outputs,etc.)*

*Insert map of stage locations. *
```{r data,include = F}
library(AnalystHelper);
library(openxlsx)
library(plyr)
library(reshape2)
# library(flextable)

library(kableExtra)
  

data.path = "./Data/"


# Reg Schedules -----------------------------------------------------------
WCA1A1=data.frame(month=c(5,7,9,12),day=c(12,8,24,1),A1=c(15.75,15.75,17.50,17.50))
WCA1A1$DOY = with(WCA1A1,as.numeric(format(date.fun(paste(1965,month,day,sep="-")),"%j")))
WCA1A2=data.frame(month=c(1,5,8,10),day=c(16,12,23,17),A2=c(17.00,15.75,15.75,17.00))
WCA1A2$DOY = with(WCA1A2,as.numeric(format(date.fun(paste(1965,month,day,sep="-")),"%j")))

WCA1 = data.frame(DOY = seq(1,366,1))|>
  merge(WCA1A1[,c("DOY","A1")],"DOY",all.x=T)|>
  merge(WCA1A2[,c("DOY","A2")],"DOY",all.x=T)|>
  mutate(A1 = dat.interp(A1),
         A2 = dat.interp(A2),
         Floor = 14)

WCA2A=data.frame(month=c(1,6,9),day=c(31,30,30),ZoneA=c(11,11,13))
WCA2A$DOY = with(WCA2A,as.numeric(format(date.fun(paste(1965,month,day,sep="-")),"%j")))

WCA2 = data.frame(DOY = seq(1,366,1))|>
  merge(WCA2A[,c("DOY","ZoneA")],"DOY",all.x=T)|>
  mutate(ZoneA = dat.interp(ZoneA),
         Floor = 10.5)

EMWL=data.frame(month=c(5,10,12),day=c(30,30,30),EMWL=c(11,12,12))
EMWL$DOY = with(EMWL,as.numeric(format(date.fun(paste(1965,month,day,sep="-")),"%j")))
WCA3.ZA=data.frame(month=c(5,10,12),day=c(30,30,30),ZoneA=c(9.5,10.5,10.5))
WCA3.ZA$DOY = with(WCA3.ZA,as.numeric(format(date.fun(paste(1965,month,day,sep="-")),"%j")))

WCA3 = data.frame(DOY = seq(1,366,1))|>
  merge(EMWL[,c("DOY","EMWL")],"DOY",all.x=T)|>
  merge(WCA3.ZA[,c("DOY","ZoneA")],"DOY",all.x=T)|>
  mutate(EMWL = dat.interp(EMWL),
         ZoneA = dat.interp(ZoneA),
         Floor = 7.5)

# Data --------------------------------------------------------------------



imodelTarget=data.frame()
for(i in 2:5){
  tmp = read.xlsx(paste0(data.path, "Increment1/Round2/20240620/iModel_Targets/20240612_only_iModelTargets_CEPPOps.xlsx"),sheet=i)
  header.vals = c("Date",unlist(tmp[1,2:ncol(tmp)]))
  if(i==2){elev.dat =data.frame(loc = unlist(tmp[1,2:ncol(tmp)]),RSMGL_Elev = unlist(tmp[2,2:ncol(tmp)]))}
  
  tmp = read.xlsx(paste0(data.path, "Increment1/Round2/20240620/iModel_Targets/20240612_only_iModelTargets_CEPPOps.xlsx"),
                     sheet=i,startRow = 6,colNames = F)
  colnames(tmp) = header.vals
  tmp$Date=date.fun(convertToDate(tmp$Date))
  tmp$Option = paste0("Option",i-1) 

  # tmp.melt = melt(tmp,id.vars = "Date",variable.name = "SITE",value.name="TARGET")
  # tmp.melt$Option = paste("Option",i-1) 
  
  imodelTarget=rbind(imodelTarget,tmp)
  print(i-1)

}

elev.dat$RSMGL_Elev[elev.dat$RSMGL_Elev==-99]=NA
elev.dat$RSMGL_Elev = as.numeric(elev.dat$RSMGL_Elev)
elev.dat = rbind(elev.dat,data.frame(loc="Avg.636465",RSMGL_Elev=7.5))
# Calcualted values
imodelTarget$Avg.636465=rowMeans(imodelTarget[,c("3A-3","3A-4","3A-28")],na.rm=T)

imodelTarget.melt = melt(imodelTarget,id.vars = c("Date","Option"),variable.name = "SITE",value.name="TARGET")

site.list = unique(imodelTarget.melt$SITE)
site.locs = data.frame(SITE = site.list,
                       LOC = c("WCA1",rep("WCA2A",3),"WCA2B",rep('WCA3A',10),"WCA3B",rep('ENP',15),rep("Structures",5),"WCA3A"))
site.locs$SITENAME = site.locs$SITE
site.locs$SITENAME = with(site.locs, ifelse(SITE=="Avg.636465","3-Gauge Avg",as.character(SITENAME)))

imodelTarget.xtab = dcast(imodelTarget.melt,Date+SITE~Option,value.var = "TARGET",mean)
imodelTarget.xtab$DOY = as.numeric(format(imodelTarget.xtab$Date,'%j'))

## variables for plotting
cols=wesanderson::wes_palette("Zissou1",4,"continuous")
opts = paste0("Option",1:4)
```

## {.tabset}

```{r loop,results='asis',echo=F,fig.width=8, fig.height=4,fig.align='center'}
# knitr::opts_chunk$set(fig.width=8, fig.height=5,fig.align='center')

# Loop to create tabset
for (i in 1:nrow(site.locs)) {
  
  tmp.dat = subset(imodelTarget.xtab,SITE==site.locs$SITE[i])
  tmp.dat.melt=melt(tmp.dat,id.vars= c('Date','DOY','SITE'),variable.name = "Option",value.name="TARGET")

  cat('###', site.locs$SITENAME[i],'\n\n')
  
  # cat("<div style='text-align: center;'>\n")
  # cat("```{r}\n\n")
  
  min.q = min(unlist(c(tmp.dat[,c(paste0("Option",1:4))],subset(elev.dat,loc==site.list[i])$RSMGL_Elev)),na.rm=T)
  min.q = round(min.q-min.q*0.025,0)
  max.q = with(tmp.dat,max(c(Option1, Option2,Option3,Option4)))
  max.q = round(max.q+max.q*0.075,0)
  
  ylim.val=c(min.q,max.q);by.y=1;ymaj=seq(ylim.val[1],ylim.val[2],by.y);ymin=seq(ylim.val[1],ylim.val[2],by.y/2)
  xlim.val=range(tmp.dat$Date);xmaj=seq(xlim.val[1],xlim.val[2],by="10 years");xmin=seq(xlim.val[1],xlim.val[2],by="1 years")
  
  par(family="serif",mar=c(1,1.5,1,1.5),oma=c(2,3,1,3));
  plot.new()
  plot(Option1~Date,tmp.dat,ylim=ylim.val,xlim=xlim.val,ann=F,axes=F,type="n")
  abline(h=ymaj,v=xmaj,lty=3,col="grey")
  for(j in 1:4){
    lines(TARGET~Date,subset(tmp.dat.melt, Option == opts[j]),col=cols[j])
  }
  abline(h=subset(elev.dat,loc==site.list[i])$RSMGL_Elev)
  axis_fun(1,xmaj,xmin,format(xmaj,"%Y"),line=-0.5)
  axis_fun(2,ymaj,ymin,ymaj)
  box(lwd=1)
  mtext(side=1,"Calender Year",line=2,cex=1.25)
  mtext(side=2,"Stage Elevation (Feet, NGVD29)",line=2.5,cex=1.25)
  mtext(side=3,adj=0,paste0(" Site: ",site.locs$SITENAME[i]," (",site.locs$LOC[i],")"))
  legend("topright",
         legend=c(paste("Option",1:4),"RSMGL Cell Elev."),
         col=c(cols,"black"),lty=c(1),lwd=c(1.5),
         pch=c(NA),pt.bg=c(NA),pt.cex = c(NA),
        ncol=2,cex=0.75,bty="n",y.intersp=1,x.intersp=0.5,xpd=NA,xjust=0.5)
  
  # cat("```\n\n")
  cat("<center>Daily Stage elevation for each option during the period of simulation.</center>\n\n")
  # cat("</div>\n\n")
  
  cat("<br>\n")
  
  # cat("```{r DOYPlot,fig.width=7,fig.height=5,fig.align='center',fig.cap='Interquantile range and median water levels summarised for the entire period of simulation. If available the current regulation schedule is provided.'}\n\n")
  
  DOY.stat = tmp.dat.melt|>
  ddply(c("DOY","Option"),summarise,
        min.val = min(TARGET),
        Q1=quantile(TARGET,probs = 0.25),
        med.val = median(TARGET),
        Q3=quantile(TARGET,probs = 0.75),
        max.val =max(TARGET),
        mean.val = mean(TARGET))

  xlim.val=c(1,366);xmaj=seq(xlim.val[1],xlim.val[2],by=90);xmin=seq(xlim.val[1],xlim.val[2],by=30)
  par(family="serif",mar=c(1,1.5,1,1.5),oma=c(2,3,1,3));
  plot(mean.val~DOY,DOY.stat,ylim=ylim.val,xlim=xlim.val,ann=F,axes=F,type="n",xaxs="i")
  abline(h=ymaj,v=xmaj,lty=3,col="grey")
  for(j in 1:4){
    with(subset(DOY.stat,Option==paste0("Option",j)),shaded.range(DOY,Q1,Q3,cols[j],lty=1))
    lines(med.val~DOY,subset(DOY.stat,Option==paste0("Option",j)),col=cols[j])
  }
  if(site.locs$LOC[i]=='WCA1'){
    lines(A2~DOY,WCA1,col="grey50",lwd=2,lty=3)
    lines(A1~DOY,WCA1,col="black",lwd=1.5)
    lines(Floor~DOY,WCA1,col="grey50",lwd=1.5,lty=2)
  }
  if(site.locs$LOC[i]=='WCA2A'){
    lines(ZoneA~DOY,WCA2,col="black",lwd=1.5)
    lines(Floor~DOY,WCA2,col="grey50",lwd=1.5,lty=2)
  }
  if(site.locs$LOC[i]=='WCA3A'){
    lines(EMWL~DOY,WCA3,col="grey50",lwd=2,lty=3)
    lines(ZoneA~DOY,WCA3,col="black",lwd=1.5)
    lines(Floor~DOY,WCA3,col="grey50",lwd=1.5,lty=2)
  }
  legend("topleft",
         legend=c(paste("Option",1:4)),
         col=c(cols,"black"),lty=c(1),lwd=c(1),
         pch=c(NA),pt.bg=c(NA),pt.cex = c(NA),
         ncol=1,cex=0.8,bty="n",y.intersp=0.9,x.intersp=0.5,xpd=NA,xjust=0.5)
  legend("topright",
         legend=c("POS IQR (Q1 - Q3)","POS Median"),
         col=c("black","grey"),lty=c(NA,1),lwd=c(1,1),
         pch=c(22,NA),pt.bg=c("grey",NA),pt.cex = c(1.5,NA),
         ncol=1,cex=1,bty="n",y.intersp=1,x.intersp=0.5,xpd=NA,xjust=0.5)
  axis_fun(1,xmaj,xmin,format(as.Date(xmaj,"%j",origin=as.Date("2016-12-31")),"%b-%d"),line=-0.5)
  axis_fun(2,ymaj,ymin,ymaj)
  box(lwd=1)
  mtext(side=1,"Month-Day",line=2,cex=1.25)
  mtext(side=2,"Stage Elevation (Feet, NGVD29)",line=2.5,cex=1.25)
  mtext(side=3,adj=0,paste0(" Site: ",site.locs$SITENAME[i]," (",site.locs$LOC[i],")"))
  # cat("```\n\n")
  
  cat("<center>Interquantile range and median water levels summarised for the entire period of simulation. If available the current regulation schedule is provided.</center>\n\n")
  
  cat("<br>\n")
  
  xlim.val=c(0,1);by.x=0.25;xmaj=seq(xlim.val[1],xlim.val[2],by.x);xmin=seq(xlim.val[1],xlim.val[2],by.x/2)
  plot(0:1,0:1,ylim=ylim.val,xlim=xlim.val,ann=F,axes=F,type="n",xaxs="i")
  abline(h=ymaj,v=xmaj,lty=3,col="grey")
  for(j in 1:4){
    sdc = ecdf_fun(subset(tmp.dat.melt, Option == opts[j])$TARGET)
    sdc$proportion = 1-sdc$proportion
    lines(value~proportion,sdc,col=cols[j])
  }
  abline(h=subset(elev.dat,loc==site.list[i])$RSMGL_Elev)
  axis_fun(2,ymaj,ymin,ymaj)
  axis_fun(1,xmaj,xmin,format(xmaj))
  box(lwd=1)
  mtext(side=1,line=2,"Proportion of Time \u2265 Stage Elevation")
  mtext(side=2,"Stage Elevation (Feet, NGVD29)",line=2.5,cex=1.25)
  mtext(side=3,adj=0,paste0(" Site: ",site.locs$SITENAME[i]," (",site.locs$LOC[i],")"))
  legend("topright",
         legend=c(paste("Option",1:4),"RSMGL Cell Elev."),
         col=c(cols,"black"),lty=c(1),lwd=c(1.5),
         pch=c(NA),pt.bg=c(NA),pt.cex = c(NA),
         ncol=1,cex=1,bty="n",y.intersp=1,x.intersp=0.5,xpd=NA,xjust=0.5)
  
  cat("<center>Stage duration curves for all options relative to ground elevation</center>\n\n")
  
  cat("<br>\n")
  
  cat("<br>\n")
    
  prop.val=seq(0.1,0.9,0.1)
  results=sapply(tmp.dat[,paste0("Option",1:4)],quantile,probs=prop.val)|>
    as.data.frame()
  results$prop.val = 1-prop.val
  results=results[order(results$prop.val),]
  rownames(results)= 1:nrow(results) 
  
  cat("<center>Table of cumulative distribution function values for each option along the stange duration curve (see above).</center>\n\n")
  
  # table1=results[,c(5,1:4)]|>
  #   flextable()|>
  #   colformat_double(j=2:5,digits=2)|>
  #   padding(padding=1.5,part="all")|>
  #   width(width=c(1.5,1,1,1,1))|>
  #   align(align = "center",part="all")|>
  #   set_header_labels("prop.val"="Prop. of Time\n\u2265 Stage Elevation",
  #                     "Option1"="Option 1",
  #                     "Option2"="Option 2",
  #                     "Option3"="Option 3",
  #                     "Option4"="Option 4")|>
  #   footnote(j=1,value=as_paragraph(paste("CDF value of iModel target elevation for site",site.locs$SITENAME[i], "in",site.locs$loc[i], "across the different options" )),
  #            ref_symbols =c(" "),part="header")
  
  cat("<center>")

  results[,c(5,1:4)]|>
    knitr::kable(col.names = c("Prop. of Time","Option 1","Option 2","Option 3","Option 4"),
                 digits=c(1,2,2,2),align="c",escape=F,full_width = T,font=15,
                 format = "html",position = "center")|>print()
 cat("</center>\n\n")
  # results[,c(5,1:4)]|>
  #   kable(col.names = c("Prop. of Time","Option 1","Option 2","Option 3","Option 4"),
  #         digits=c(1,2,2,2),align="c",escape=F)|>
  #   # kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
  #   kable_classic(full_width = F, html_font = "Cambria",font=14)|>
  #   footnote(general = paste("CDF value of iModel target elevation for site",site.locs$SITENAME[i], "in",site.locs$LOC[i], "across the different options" ))

  cat("<br>\n\n")
  
}
```

<br>
